Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-03 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

\noindent Given a state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
for any 1-dimensional projector~$\proj{\psi}$. Since the maximum
length of the intervals in $\mathscr{I}_{n}$ is $1/n$, it is the
upper bound of the difference $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
 This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$ by
definition.

>>>>

\noindent Given a state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
for any 1-dimensional projector~$\proj{\psi}$. Since the maximum
length of the intervals in $\mathscr{I}_{n}$ is $1/n$, it is also
the upper bound of the difference $\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
 This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$ by
definition.
